Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-08-10 Tex/Paper.tex
Compined transverse phasespace plots to one figure

@@

\begin{figure*}[hbt]
    \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
    \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
    \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
    \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
    \\
    \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
    \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
    \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
    \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
        plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
        particles and lines represent particles with position $1.40 < \xi < 1.42$. The red particles and lines
        represent particles with position $1.55 < \xi < 1.57$.}
\end{figure*}

>>>>

\begin{figure*}[hbt]
    \includegraphics[width=\linewidth,trim={0mm 0mm 0mm 0mm},clip]{figures/beamFilamentationAll}
    %~ \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
    %~ \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
    %~ \\
    %~ \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
    %~ \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
        plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
        particles and lines represent particles with position $1.40 < \xi < 1.42$. The red particles and lines
        represent particles with position $1.55 < \xi < 1.57$.}
\end{figure*}

@@
